Asimilación de distintas observaciones

### 2020-10-23 analysis/chapters/experimento_20181122.Rmd
Arreglo viento

```{r q-wind, warning=FALSE, fig.align="center", fig.height=4, fig.width=6, message=FALSE,}
fcsts <- expand_grid(fcsts = c("20181122000000", "20181122060000"),
                     exp = c("E4", "E5", "E6", "E7"))

@@

q[bottom_top <= 7, .(q = mean(q), u = u[bottom_top == 1], v = v[bottom_top == 1]), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[coord, on = c("south_north", "west_east")] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(lon, lat)) +
  geom_point(aes(color = q*1000)) +
  scale_color_distiller(name = NULL,
                        palette = "BrBG", direction = 1,
                        breaks = seq(0, 0.02, 0.002)*1000,
                        guide = guide_colorstrip(inside = FALSE,
                                                 barwidth = 30,
                                                 barheight = 0.8)) +
  geom_vector(aes(dx = u, dy = v), data = function(x) x[is.cross(south_north, west_east, 5)]) +
  scale_mag() +
  geom_sf(data = map, inherit.aes = FALSE, color = "black", fill = NA, size = 0.2) +
  coord_sf(xlim = range(coord$lon), ylim = range(coord$lat)) +
  facet_grid(date ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Low level humidity (g/Kg)",
       x = "Longituted",
       y = "Latitude") +
  theme_minimal(base_size = 16) +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

>>>>

```{r q-wind, warning=FALSE, fig.align="center", fig.height=5, fig.width=9, message=FALSE,dev="png"}
fcsts <- expand_grid(fcsts = c("20181122000000", "20181122060000"),
                     exp = c("E4", "E5", "E6", "E7"))

@@

q[bottom_top <= 7, .(q = mean(q), u = u[bottom_top == 1], v = v[bottom_top == 1]), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[coord, on = c("south_north", "west_east")] %>% 
  .[, date := factor(date)] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = q*1000), proj = norargentina_lambert,
                    breaks = seq(0, 0.02, 0.002)*1000) +
  scale_fill_distiller(name = NULL,
                        palette = "BrBG", direction = 1,
                        breaks = seq(0, 0.02, 0.002)*1000,
                        guide = guide_colorstrip(inside = FALSE,
                                                 barwidth = 25,
                                                 barheight = 0.8)) +
  # geom_vector(aes(x = lon, y = lat,
  #                 dx = u, dy = v), data = function(x) x[is.cross(y, x, 8)],
  #             arrow.angle = 12, size = 0.3) +
  # scale_mag() +
  geom_sf(data = map, inherit.aes = FALSE, color = "black", fill = NA, size = 0.2) +
  coord_sf(xlim = range(coord$lon), ylim = range(coord$lat)) +
  facet_grid(date ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Low level humidity (g/Kg)",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```
